---
title: "ridgereg"
author: "Chathuranga Silva, Mohammed Bakheet, and Nikodimos Gezahegn"
date: "27th October 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ridgereg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RBonusLab)
library(caret)
library(mlbench)
library(ggplot2)
library(e1071)
```
## Using BostonHousing data  
```{r BostonHousing}
data("BostonHousing")
housing <- BostonHousing
str(housing)
summary(housing)
```
## Data Cleaning  
```{r BostonHousing2}
library("Amelia")
#Check for any NA’s in the dataframe.
missmap(housing,col=c('yellow','black'),y.at=1,y.labels='',legend=TRUE)

```

## Data Visualization with CorrPlots  
```{r Visualization}
library("corrplot")
library("dplyr")
corrplot(cor(select(housing,-chas)))
```

## Spiliting data into training and testing  
```{r dataSpliting}
library("caTools")
set.seed(123)
#Split the data , `split()` assigns a booleans to a new column based on the SplitRatio specified. 
split <- sample.split(housing,SplitRatio =0.75)
train <- subset(housing,split==TRUE)
test <- subset(housing,split==FALSE)
```

## Fitting ridge regression model Using Ridgereg With Four Parameters
```{r ModelBuildingRidgereg}
model <- ridgereg(formula = medv ~ crim + rm + tax + lstat, data = train)
summary(model)
#The model with three parameters
model <- ridgereg(medv ~ crim + rm + tax, data = train)
summary(model)
#The model with two parameters
model <- ridgereg(medv ~ crim + rm, data = train)
summary(model)
```

## Model Building and Training Using Forward Selection and lm function
```{r ModelBuildingForward}
model <- lm(medv ~ 1, data = train)
step(model, direction = "forward", scope = formula(model))
summary(model)
```

<!-- ## Model Building and Training -->
<!-- ```{r ModelBuilding} -->
<!-- model <- lm(medv ~ crim + rm + tax + lstat, data = train) -->
<!-- summary(model) -->
<!-- ``` -->

## Model Visualization  
```{r ModelVisualziation}
res <- residuals(model)
# Convert residuals to a DataFrame 
res <- as.data.frame(res)
ggplot(res,aes(res)) +  geom_histogram(fill='blue',alpha=0.5)
plot(model)
```

## Testing the model using our testing dataset
```{r ModelTesting}
library("plotly")
test$predicted.medv <- predict(model,test)
pl1 <-test %>% 
  ggplot(aes(medv,predicted.medv)) +
  geom_point(alpha=0.5) + 
  stat_smooth(aes(colour='black')) +
  xlab('Actual value of medv') +
  ylab('Predicted value of medv')+
  theme_bw()

ggplotly(pl1)
```

## Model Assessment
```{r ModelAssessment}
error <- test$medv-test$predicted.medv
rmse <- sqrt(mean(error)^2)
print(rmse)
```





## Using createDataPartition function to spilit data into training and testing datasets
```{r BostonHousingNext}

partitioining <- createDataPartition(
  y = BostonHousing$zn,
  ## the outcome data are needed
  p = .75,
  ## The percentage of data in the
  ## training set
  list = FALSE
)
#Spliting BostonHousing data into training and testing datasets
training <- BostonHousing[ partitioining,]
testing  <- BostonHousing[-partitioining,]
nrow(training)
nrow(testing)

```
## How to use ridgereg function
```{r ridgereg}
data("iris")
ridgereg(Petal.Length ~ Sepal.Width + Sepal.Length,data = iris)
```
## using caret package
```{r caret}
data(Sonar)

set.seed(107)
inTrain <- createDataPartition(
  y = Sonar$Class,
  ## the outcome data are needed
  p = .75,
  ## The percentage of data in the
  ## training set
  list = FALSE
)
## The format of the results

## The output is a set of integers for the rows of Sonar
## that belong in the training set.
str(inTrain)
## Spliting data into training and testing
training <- Sonar[ inTrain,]
testing  <- Sonar[-inTrain,]
nrow(training)
nrow(testing)

## Training the model
# plsFit <- train(
#   Class ~ .,
#   data = training,
#   method = "pls",
#   preProc = c("center", "scale"),
#   ## added:
#   tuneLength = 15
# )
```
## Find the best hyperparameter value for λ using 10-fold cross-validation on the training set

```{r training}

mod <- trainControl(method = "repeatedcv", number = 10, repeats = 10)
```
